Panel Seminars

### 2021-11-05 choosing-population-genetics.Rmd
Edited WGS intro

1) High coverage individual whole genome resequencing (hcWGS)  
 i) Whole-genome resequencing (WGS) is where whole genomes of multiple individuals are sequenced and mapped to an assembled reference genome in order to compare variable sites between individuals or populations. Sequence coverage refers to the average number of sequencing reads per region of the genome. With more sequencing reads at a region (higher coverage), errors that arise during sequencing have a smaller impact on accurately identifying variable sites (termed "genotyping").  
2) Low coverage individual WGS (lcWGS)  
 i) 
3) pooled individuals (Poolseq)  
4) reduced-representation sequencing 
 i) can be split into restriction-based methods (eg RADseq) and targeted capture methods (eg exome capture)

>>>>

### 1) High coverage individual whole genome resequencing (hcWGS)  {.unlisted .unnumbered}
**Whole-genome resequencing (WGS)** is where whole genomes of multiple individuals are sequenced and mapped to an assembled reference genome in order to compare variable sites between individuals or populations. **Coverage depth** refers to the average number of sequencing reads per region of the genome. With more sequencing reads at a region (higher coverage depth), errors that arise during sequencing have a smaller impact on accurately identifying variable sites (termed "genotyping") (cite).

### 2) Low coverage individual WGS (lcWGS)  {.unlisted .unnumbered}
Low coverage whole genome sequencing is where whole genomes of many individuals are sequenced, but depth of coverage so low that individual genotypes cannot be confidently assigned (cite). Instead of assigning specific, "hard called genotypes, lcWGS data requires probabilistic analyses that account for uncertainty about the true genotype and can incororate uncertanty accross all sequenced samples. Typically, sequencing depth of > 3 reads is considered "low coverage".

### 3) Reduced-representation sequencing {.unlisted .unnumbered}
As the name suggests, this approach aims to sequence a reduced portion of the genome across multiple individuals at moderate to high coverage for variant discovery and genotyping with high confidence. The genome fragments can be selected at random, or through targeted probe assays.
#### RADseq/Genotype-by-sequencing  {.unlisted .unnumbered}
This very popular class of methods involve sequencing a subset of genomic regions randomly distributed throughout the genome, often using restriction enzymes (i.e., RADseq: restriction site-associated DNA). 
#### Targeted capture methods (e.g., exome capture)  {.unlisted .unnumbered}

### 4) Pooled individuals (Poolseq)  {.unlisted .unnumbered}

![Figure 1 from Lou et al. 2021 comparing the distribution of sequencing reads mapped to a reference genome.](images/mec16077-fig-0001-m.jpg)

### 2021-11-05 index.Rmd
Edited WGS intro

# BETA TEST OF SITE!

@@

On this website you will find a collection of guidelines, tutorials, recommended readings, and method evaluations for various 'omics analyses that are commonly used in studies of nonmodel systems (particularly marine species). Instead of providing rigid "best practices", we aim to encourage data exploration and rigorous quality control through "best practices".

Based on the expertise of the working group, we have developed content for these topics:

@@

## Panel Seminars 
To facilitate discussions about practices and pitfalls in applying 'omics to non-model systems, we hosted [Q & A panel seminars](panels.html) with experts on topics ranging from RADseq, population genomics with WGS, and transcriptomics. Check them out on [YouTube](https://www.youtube.com/channel/UCosG6JfIj7k0DizfsD5ADfQ)!

>>>>

@@

On this website you will find a growing and evolving collection of guidelines, tutorials, recommended readings, and method evaluations for various 'omics analyses that are commonly used in studies of nonmodel systems (particularly marine species). Instead of providing rigid "best practices", we aim to encourage data exploration and rigorous quality control through "best principles". The guidelines are written by members of the MarineOmics working group or the community, then shared for peer review. Comments on current website content or suggestions for new content can be made through the [Discussion Forum](discussion.html).

Based on the expertise of the MarineOmics working group, the first topics include:

@@

### The guidelines portion of the website is still under peer review and should be considered a "preprint". If you are interested in contributing to the peer review process, check out the [Discussion Forum](discussion.html). {.unlisted .unnumbered}

# Panel Seminars 
To facilitate discussions about practices and pitfalls in applying 'omics to non-model systems, we hosted [Q & A panel seminars](panels.html) with experts on topics ranging from RADseq, population genomics with WGS, and transcriptomics. Check them out on [YouTube](https://www.youtube.com/channel/UCosG6JfIj7k0DizfsD5ADfQ)!
